---
title: "Plotly examples"
author: "Xin Fang"
output: 
  html_document:
    toc: true
    toc_float: true
---

#load and clean data

We're going to look at NYC restaurant inspection data. Since this data set is big, we are only going to look at my favorite restaurant types (i.e. Chinese, Korean, Thai, French, Mexican, and Japanese) in Manhattan. 

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)
library(lubridate)
library(plotly)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d 

knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  warning = F 
  )
```

```{r}
data("rest_inspec")

rest_inspec <- rest_inspec %>% 
  select(boro, cuisine_description,  dba, score, grade, critical_flag) %>% 
  filter(grade %in% c("A", "B", "C"), 
         cuisine_description == c("Korean", "Chinese", "Japanese", "Thai", "French", "Mexican"), 
         boro == "MANHATTAN", 
         critical_flag != "Not Applicable") %>% 
  drop_na(score)
```
This rest_inspec dataset now contains `r nrow(rest_inspec)` observations. It is seems reasonable to make plots now. 

# plotly plots 

## Bar plot
```{r}
rest_inspec %>% 
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n), 
         text_label = str_c("Cuisine: ", cuisine_description, "\nN = ", n)) %>% 
  plot_ly(x = ~cuisine_description, y = ~n, color = ~cuisine_description,text = ~text_label,
          type = "bar", mode = "markers") %>% 
  layout(
    title = "Count of restaurants in Manhattan by cuisine", 
    xaxis = list(title = "Cuisine"),
    yaxis = list(title = "Count"))
```

## boxplot 
```{r}
rest_inspec %>% 
  mutate(text_label = str_c("Cuisine: ", cuisine_description, "\nScore: ", score)) %>%
  plot_ly(y = ~score, x = ~cuisine_description, 
          color = ~cuisine_description, 
          text = ~text_label,
          type = "box") %>% 
  layout(
    title = "Scores of restaurants in Manhattan grouped by my favorite cuisine types", 
    xaxis = list(title = "Cuisine types"),
    yaxis = list(title = "Inspection score"))
```


## Histogram
```{r}
rest_inspec %>% 
  mutate(text_label = str_c("Restaurant: ", dba, "\nScore: ", score)) %>%
  plot_ly(x = ~score, type = "histogram", alpha = .8, text = ~text_label,mode = "markers") %>% 
  layout(title = "Histogram of inspection scores of NY restaurants",
         xaxis = list(title = "Score"),
         yaxis = list(title = "Count"))
```